Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-18 writeup/gz_hubble_data.tex
Remove reference to Johnson+15 on distraction bias

The approach used in GZH for correcting the weighted classifications for redshift
bias rests on the assumption that the \emph{degree} of bias is a function of
the apparent size and brightness of the image as seen on screen. This is
controlled by two types of parameters: \textbf{intrinsic} properties of the
galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. There may also be other parameters that affect
classifier accuracy, such as the proximity of close companions \citep[``distraction
bias''; see][]{joh15} or bias as a function of individual classifier ability and
skill. The combination of all such parameters forms a high-dimensional space,
and it is not clear how to separate this into individual effects. Instead, the
method used here employs only two parameters intended to capture the bulk of
the change in bias: the $r^\prime$-band surface brightness ($\mu_r$; intrinsic)
and redshift ($z$; extrinsic).

>>>>

The approach used in GZH for correcting the weighted classifications for
redshift bias rests on the assumption that the \emph{degree} of bias is a
function of the apparent size and brightness of the image as seen on screen.
This is controlled by two types of parameters: \textbf{intrinsic} properties of
the galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. There may also be other parameters that affect
classifier accuracy, such as the proximity of close companions or bias as a
function of individual classifier ability and skill. The combination of all
such parameters forms a high-dimensional space, and it is not clear how to
separate this into individual effects. Instead, the method used here employs
only two parameters intended to capture the bulk of the change in bias: the
$r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$;
extrinsic).
